Quantitative Auditing of AI Fairness with differentially private Synthetic Data

### 2024-12-11 paper/paper.tex
progress

% TODO: add compas example in the following

@@

For security, it creates a point of vulnerability of unauthorized access, and the auditor is now a target of data security attacks. The auditor may not have the necessary resources to defend against these threats. A breach at the auditor's end could result in compromises of individuals' sensitive information.

As for privacy, on the other hand, it introduces risks of information leakage. Releasings of analyses on real data may inadvertently reveal sensitive information by data inference attacks. Attackers can exploit data patterns in outputs or combine outputs with external data to infer sensitive information.

>>>>

@@

For security, it creates a point of vulnerability to unauthorized access, and the auditor is now a target of data security attacks. The auditor may not have the necessary resources to defend against these threats. A breach at the auditor's end could result in compromises of individuals' sensitive information. In the COMPAS example, had the data not been public already, ProPublica may be targeted by hackers to access the sensitive criminal justice data.

As for privacy, on the other hand, it introduces risks of information leakage. Releasing analyses of real data may inadvertently reveal sensitive information through data inference attacks. Attackers can exploit data patterns in outputs or combine outputs with external data to infer sensitive information. In the COMPAS example, had the data not been public already, their analyses may inadvertently reveal the identities of individuals in the criminal justice system.
